Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-05-09 Paper.Rmd
The journey conts again

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Customer Reviews (OCR). Online Customer Reviews come in the form of electronic word-of-mouth (EVOM) @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010. OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011]. \###(need different citations here!!!)\###

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type @10.2307/1830691.

@@

-   The research on perceived helpfulness is still growing and there is no consensus on neither about methodology nor about important independent variables. In fact, there are conflicting results in the literature. Thus, creating a need for more analyses on different and unique data sets.

@@

-

@@

-   Give the background of perceived helpfulness

@@

# Data

@@

@@

>>>>

Online shopping has becoming more and more prevalent in average consumer's daily life. Electronic shopping brought many advantages both for sellers and buyers. One of the positive perks is Online Customer Reviews (OCR). Online Customer Reviews come in the form of electronic word-of-mouth @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010. OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011]. \###(need different citations here!!!)\###

OCR help customers by decreasing their search costs. Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product. This information acquiring process is costly. Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691. Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop). On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).

@@

The research on perceived helpfulness is still growing. In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature @hunter1991. In this case, the study on perceived helpfulness is not an exception. Because of this reason, We think more empirical studies on perceived helpfulness are required. This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.

@@

-   Outline the paper

@@

-   mention moderating effects of product type for every variable

The research on Online Customer Reviews could be considered to have two main branches. One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012]. The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only. Of course, the boundary between these two branches are somewhat blurry and same independent variables were used to explain both helpfulness and sales. Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales. Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018]. Thus, these two branches are inter-connected with each other. This paper tries to understand behavioral aspect.

Many independent variables and their relationship between perceived helpfulness was examined by researchers. Hong et al. (2017) @hong2017 groups these independent variables into two chunks. The first group is reviewer-related predictors. Variables within this group tries to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.). [@sun2019; @ghose2011]. The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018]. Ghose et al. (2011) @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones. The choice of the variables is of course heavily dependent on the data itself. In this paper, we only examined review-related predictors.

Review Length(Depth) could be considered as one of the most important independent variable explaining perceived helpfulness. It might be implemented in different ways but for the majority of the studies it is the word count in a given review. For most of the researchers, longer reviews contain more information about the product. As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020]. However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015]. Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].

Review Rating (Review Extremity) is another important identifier of perceived helpfulness. This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product. It's effect on perceived helpfulness is rather divergent in the literature. A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness. Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[ @mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006]. In other studies, linear positive relationship was found. In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020]. There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].

Review Age is an indicator of how long the time passed after a review published on a web site. On some papers the opposite of Review Age, Review Freshness could be employed as well. Different effects on perceived helpfulness were also observed by researchers. Some researchers discussed that a timely review is very important at conveying the true information about a certain product [@liu2014; @li2019; @zhou2019]. Others discussed that some web sites promotes newer reviews and because of that more recent reviews are more helpful [@lee2014; @choi2020; @wu2021].

-   mention negative positive words here

@@

@@

## Data Collection

## Variables and EDA

## Method

@@

# References
